The Folly of Password Policies: The case for organisations implementing technical alternatives over trying to manage users

### 2014-12-15 paper.tex
More trimming

\textcite{herley2009so} argued that users rationally reject costs
placed upon them from security policies. He invokes Kuhn's
``Paradigm Shift''\parencite{kuhn1962structure} to suggest
that the increasing burden placed on users with every attack
that takes place and the additional complexity that comes
therewith may hint at an imminent, yet dramatic change in
how users are asked to authenticate. It is yet to be seen
if Kuhn's observations of sudden shifts of thinking
in the scientific community apply to a more general
user base such as employees or indeed the general public, but
a strong need for change can be taken from the analogy
at least.

@@

In the next few sections, we look at various aspects
of password security, how users are normally advised
and critically examine the effectiveness of that advice.

>>>>

\textcite{herley2009so} argued that users rationally reject costs
placed upon them from security policies. He invokes Kuhn's
``Paradigm Shift''\parencite{kuhn1962structure} to suggest
an imminent, yet dramatic change in
how users are asked to authenticate as the complexity of
rules placed on users increases with each attack.

@@
